\begin{document}
    Please provide all of the information requested below. Incomplete information can delay the
    processing of your application. \textbf{Please print clearly.}
    
    It is also helpful to authorize employees, bank, and landlords to release all relevant information
    to \highlight{((( contract.agencyShortName )))} prior to submitting this application.
    
    \section{Occupant Information}
        \formLine[((( contract.applicant.name )))]{Name}
        \formLine{Social Security Number}
        \formLine{Driver's License Number}
        \formLine{Date of Birth}
        \formLine[((( contract.applicant.phone )))]{Home Phone}
        \formLine{Work Phone (optional)}
        \formLine[((( contract.applicant.email )))]{Email}
    
    \section{Employment History}
        \formLine{Current Employer}
        \formLine{Address}
        \formLine{City, State, Zip}
        \formLine{Phone}
        \formLine{Supervisor}
        \formLine{Position}
        \formLine{How Long}
        \formLine{Salary}
        
    \section{Rental History}
    \sectionintro{Please provide at least two years of information.}
        \subsection{Present Address}
            \formLine[((( contract.applicant.address )))]{Address}
            \formLine{Did you rent or own?}
            \formLine{Amount paid monthly}
            \formLine{Reason for leaving}
            \formLine{Landlord or Mortgage Company Name}
            \formLine{Phone}
    
        \subsection{Previous Address}
            \formLine{Address}
            \formLine{Did you rent or own?}
            \formLine{Amount paid monthly}
            \formLine{Reason for leaving}
            \formLine{Landlord or Mortgage Company Name}
            \formLine{Phone}
    
    \section{Banking Reference}
        \formLine{Name}
        \formLine{Phone}
        \formLine{Address}
        \formLine{Account Number}
        \formLine{Checking or Savings?}
        \formLine{Balance}
    
    \section{Personal References}
        \subsection{Reference 1}
        \formLine{Name}
        \formLine{Address}
        \formLine{City, State, Zip}
        \formLine{Relationship}
        \formLine{Phone}
    
        \subsection{Reference 2}
        \formLine{Name}
        \formLine{Address}
        \formLine{City, State, Zip}
        \formLine{Relationship}
        \formLine{Phone}
    
        
    \section{Other Information}
        \formLine{Pets (describe)}
        \formLine{Water-filled furniture (describe)}
        \formLine{Vehicles/boats to be parked on premises (make/model/year/license no.)}
        \formLine{In the past, have you been delinquent in paying rent or other financial obligations?}
        ((( contract.formLineMulti(2,'If yes, please explain') )))
        \formLine{In the past, have you failed to perform any obligations of a rental agreement or have you been a defendant in an eviction lawsuit?}
        ((( contract.formLineMulti(2,'If yes, please explain') )))
    
    %\pagebreak
    \section{Agreement and Authorization}
        \subsection{Consumer Report Disclosure}
            \clause[Eligibility]{The following items will be considered to determine
                eligibility for residency:
                \begin{itemize}
                    \item Social Security Number validation, including verification of matching birth date
                    \item Previous or alternate names
                    \item Previous addresses
                    \item Criminal records, including county, state, OFAC/Patriot Act, and Sex Offender Registry
                    \item Civil records, including bankruptcies, liens, judgments, and evictions
                    \item Verification of current employment
                    \item Verification of previous rental history or reference
                    \item Satisfactory level of credit worthiness based on your credit report and FICO score
                \end{itemize}
            }
            \clause[Derogatory Information]{Derogatory information found while researching any of these items 
                may result in denial of your application, or the requirement of an increased deposit, qualified
                guarantor, last month’s rent, increased monthly rent, and/or other measures to secure your
                residency.}
            \clause[((( contract.agencyShortName )))]{
                To investigate your background and/or credit, a Consumer Report will be obtained from:
                \begin{center}
                    ((( contract.agencyContactInformation )))
                \end{center}
            }
            \clause[Applicant's Rights]{The Consumer Reporting Agency's role is to provide us with 
                character background related information about you. Therefore, they will be unable to 
                supply the reasons why you may be denied residency. Should you be denied or required to
                additionally secure your residency, you have the right to request a copy of your consumer
                report free of charge, within sixty (60) days from the date you receive an Adverse Action
                Notice. You also have the right to dispute the accuracy or completeness of any item on
                your consumer report by contacting the Consumer Reporting Agency using the information
                displayed above.}
    
        \subsection{Signature}
            \clause{I hereby acknowledge that the information on this application is true and
                correct to the best of my knowledge. I understand all terms in this application, and 
                I authorize \highlight{((( contract.lessorNames )))} to
                verify the above information and obtain consumer or investigative credit report, criminal 
                background report, and/or eviction records from ((( contract.agencyShortName ))). 
                I understand that the \highlight{((( contract.applicationFee|escapeTex )))} 
                fee for verifying this rental application is not a deposit, will not be applied to any rent, 
                or refunded even if the application to rent is declined.}

    ((( contract.getSignatureFormlines() )))
    
    \section{For Office Use Only}
        ((( contract.formLineMulti(3,'Remarks') )))
        \formLine{Move in date}
        \formLine{Unit}
        \formLine{Unit Type}
        \formLine{Rent}
\end{document}
